%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\blueHref}[2]{\href{#1}{\color{blue} #2}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Vladimir Rachkin} & Email : \href{mailto:vova@kpnn.ru}{vova@kpnn.ru}\\
  \href{https://github.com/robozmey}{https://github.com/robozmey} & Mobile : +79029190973 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  	\resumeSubheading
      {School of data analysis (Yandex)}{Saint Petersburg, Russia}
      {Machine learning}{Sep. 2022 -- Present}
    \resumeSubheading
      {Saint Petersburg State University}{Saint Petersburg, Russia}
      {Bachelor of Computer Science  }{Sep. 2020 -- Present}
    \resumeSubheading
      {Physics and mathematics class of SFU in Lyceum 7}{Krasnoyarsk, Russia}
      {High School  }{Sep. 2018 -- June 2020}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Selected projects}
  \resumeSubHeadingListStart
  	\resumeSubItem{\blueHref{https://github.com/robozmey/Yenisey}{Yenisey}}
      {Base for videogame engine in development written on \textbf{C++} with 				\textbf{OpenGL}. Created as university assignment.}
  	\resumeSubItem{\blueHref{https://github.com/robozmey/unELFer}{UnELFer}}
      {Disassembler for RISC-V. An university assignment written in \textbf{C++}.}
    \resumeSubItem{Lambda Calculus}
      {A program that can $\beta$-reduce lambda terms and check their $\alpha\beta$-equivalence. An university assignment written in \textbf{Haskell}.}
    \resumeSubItem{\blueHref{https://github.com/robozmey/matlog-formulas}{Formula Normalizer}}
      {A simple program that translates formulas into some normal forms. An university assignment written in \textbf{Haskell}.}
%    \resumeSubItem{\href{https://github.com/SmnTin/simple-type-checker/tree/system-f}{System F}}
%      {Type checker for Church-style Polymorphic Lambda Calculus (System F). An assignment written in \textbf{Haskell}.}
    \resumeSubItem{{Olympiad results email sender}}
      {Tool that sends out the verified works to the participants via e-mail. A task from organizer of the ROI-regional written in \textbf{C++ with QT}.}
     \resumeSubItem{\blueHref{https://github.com/robozmey/phoenix_proof}{Phoenix Proof}}
      {TLA+ specification for \blueHref{https://arxiv.org/abs/2106.01240}{Phoenix Vault} smart contract. \textbf{TLA+}}{}
%    \resumeSubItem{\href{https://github.com/robozmey/haskell-nengine}{Nengine}}{N-dimensional engine for videogames. My project written in \textbf{Haskell}.}
    \resumeSubItem{\blueHref{https://github.com/robozmey/paperwar}{PaperWar}}{Online web-game, with two teams fight for generator. Main feature: only one stat - power, witch uses as for regeneration as for shooting. My project written in \textbf{NodeJS}.}

  \resumeSubHeadingListEnd
  %-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  	\resumeSubheading{Internship in Yandex}
      {Saint-Petersburg}{MySQL database modification}{2022}
      
    \resumeSubheading{Internship in ABS}
      {Krasnoyarsk}{Addon for 1C-Accounting}{2018}

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C, C++, Haskell, Python, JavaScript, SQL, Rust, Kotlin }
    }
    \item{
      \textbf{Technologies}{: OpenGL, OpenCV, OpenCL, PyTorch, 1C }
    }
  \resumeSubHeadingListEnd

%--------EXTRACURRICULAR ACTIVITIES------------
\section{Extracurricular Activities}
  \resumeSubHeadingListStart
    \resumeSubheading{Member of the organizing committee of the regional stage of the ROI}{}
      {Basically, scanning and sending verified works to participants. Also assistance in organizing.}{Winter 2021}
  \resumeSubHeadingListEnd

%-----------ACADEMIC ACHIEVEMENTS-----------------
\section{Academic Achievements}
  \resumeSubHeadingListStart
    \resumeSubheading{All-Russian School Olympiad in Informatics}{Russia}
    {2nd degree diploma in finals. There are usually several million participants over all the stages.}{2020}
%    \resumeSubheading{All-Siberia Olympiad for Schoolchildren in Informatics}{Russia}
%    {Finalist.}{2020}
    \resumeSubheading{Open Olympiad in Informatics}{Moskow, Russia}
    {Finalist.}{2020}
    \resumeSubheading{Open Olympiad for Schoolchildren "Information Technologies"}{Russia}
    {Winner.}{2019}
    \resumeSubheading{Kvantoriada-2017}{Skolkovo, Russia}
    {Finalist.}{2017}
    \resumeSubheading{World Robot Conference}{Bejing, China}
    {Participant.}{2015}
    \resumeSubheading{Russian Robot Olympiad}{Innopolis, Russia}
    {2nd degree diploma in finals.}{2015}

  \resumeSubHeadingListEnd

%-------------------------------------------

\end{document}